Computing volume via non-uniform rectangular infinitesimals

### 2019-08-16 Cav2D/article-template.tex
captions to figures

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{prismatoid.pdf}
\caption{The solid depicted in Figure~\ref{fig:prismatoid_solid} is a prismatoid. We can, therefore, calculate its volume with the prismatoid volume equation: $V_{\mathcal{S}}$. If the 
areas of the two parallel faces are A1 and A3, the cross-sectional area of the intersection of the prismatoid with a plane midway between the two parallel faces is A2, 
and the height (the distance between the two parallel faces) is h, then the volume of the prismatoid is given by  }
\label{fig:prismatoid}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_solid.pdf}
\caption{xx}
\label{fig:sphere_solid}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_regions.pdf}
\caption{xx}
\label{fig:sphere_regions}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
\caption{xx}
\label{fig:sphere_xy}
\end{figure}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{prismatoid.pdf}
\caption{Another depiction of the solid $\mathcal{S}$ found in Figure~\ref{fig:prismatoid_solid} which highlights the fact that $\mathcal{S}$ is a prismatoid. We can, therefore, calculate its volume with the prismatoid volume equation: $V_{\mathcal{S}}= \frac{h}{6}(A_1+4A_2+A_3)$.
Note, the area of the two basis of $\mathcal{S}$ are denoted by $A1$ and $A3$, the cross-sectional area of the intersection of $\mathcal{S}$ with a plane midway between the two basis is denoted via $A2$, 
and the height of $\mathcal{S}$ is denoted by $h$. Moreover, also note that the surfaces associated with $A1$, $A2$ and $A3$ are depicted in the above figure using shaded sheets. For $\mathcal{S}$ 
$A1=$, $A2=$, $A3 = $ and $h=$. The volume of $\mathcal{S}$ is, therefore, $25.6$.}
\label{fig:prismatoid}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_solid.pdf}
\caption{The solid $\mathcal{S}$ which is bounded by the planes $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane.}
\label{fig:sphere_solid}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_regions.pdf}
\caption{The transformation $T$ associated with the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid}.}
\label{fig:sphere_regions}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
\caption{The $xy$-projection of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} onto the $xy$-plane.}
\label{fig:sphere_xy}
\end{figure}
